Log or not - Analysis of ECDC forecasts

### 2022-01-30 analysis/Analysis ECDC forecasts.Rmd
add plot with mean vs. var of observed values

>>>>

## Mean vs. sd of observed values

```{r}

label_fn <- function(x) {
  ifelse(x < 1000, 
         paste(x), 
         ifelse(x < 1e6, 
                paste0(x / 1000, "k"),
                ifelse(x < 1e9, 
                       paste0(x / 1e6, "m"), 
                       paste0(x / 1e9, "b"))
                )
         )
}

hub_data |>
  select(location, target_type, target_end_date, true_value) |>
  unique() |>
  group_by(location, target_type) |>
  summarise(mean_value = mean(true_value), 
            sd_value = sd(true_value), 
            var_value = var(true_value)) |>
  ggplot(aes(y = var_value, x = mean_value)) +
  geom_point() + 
  facet_wrap(~ target_type, scales = "free") + 
  scale_x_continuous(trans = "log10", labels = label_fn) +
  scale_y_continuous(trans = "log10", labels = label_fn) +
  # scale_x_continuous(labels = label_fn) +
  # scale_y_continuous(labels = label_fn) +
  labs(y = "Variance observed value", x = "Mean observed value") + 
  geom_function(fun = function(x) x^2, linetype = "dashed", size = 0.5) + 
  theme_minimal()

ggsave("output/figures/HUB-mean-var-obs.png", width = 7, height = 4)
